Multimatrices and Their Derivatives

### 2019-06-24 Math/paper.tex
Adding some arguments.

@@

\begin{displayquote}
``You can't just start a section with a subsection heading. At least put a quote
in there or something,'' - Dr. William Tepfenhart 
\end{displayquote}

@@

In other words, let $s \in \mathbb{R}$ and $S \in \mathbb{R}^{\left<\right>}$ such that
$S[\left<\right>] = s$. Then, for any multimatrix $A$, 
\[ sA = As = S \mmult{0} A = A \mmult{0} S \]
\end{theorem}
\begin{proof}
Let $|A| = \vec{a}$. Then for all $\bar{a} \in \Dim(\vec{a})$,
\begin{align*}
	(sA)[\bar{a}]
	&= (s)A[\bar{a}] \\
	&= A[\bar{a}](s) \\
	&= (As)[\bar{a}]
\end{align*}
So $sA = As$. Also,
\begin{align}
	(sA)[\bar{a}]
	&= (s)A[\bar{a}] \\
	&= S[\left<\right>]A[\bar{a}] \\
	&= \sum_{\forall \bar{c} \in \Dim(\left<\right>)}
		S[\left<\right> \oplus \bar{c}]A[\bar{c} \oplus \bar{a}] \\
	&= (S \mmult{0} A)[\left<\right> \oplus \bar{a}] \\
	&= (S \mmult{0} A)[\bar{a}] \\
\end{align}
Note that step 3 is valid because $\bar{c}$ can only be $\left<\right>$ and
$\left<\right> \oplus \bar{a} = \bar{a}$. So, $sA = S \mmult{0} A$.
Finally, by similiar reasoning,
\begin{align*}
	(sA)[\bar{a}]
	&= (s)A[\bar{a}] \\
	&= A[\bar{a}](s) \\
	&= A[\bar{a}]S[\left<\right>] \\
	&= \sum_{\forall \bar{c} \in \Dim(\left<\right>)}
		A[\bar{a} \oplus \bar{c}] S[\bar{c} \oplus \left<\right>] \\
	&= (A \mmult{0} S)[\bar{a} \oplus \left<\right>] \\
	&= (A \mmult{0} S)[\bar{a}]
\end{align*}
So $sA = A \mmult{0} S$. Therefore we've shown that
$sA = As = S \mmult{0} A = A \mmult{0} S$
\end{proof}

@@

Let $F(x)$ be a function $F : \mathbb{R} \to \mathbb{R}^{\vec{f}}$. And let
$G(X)$ be an equivalent function,
$G : \mathbb{R}^{\left<\right>} \to \mathbb{R}^{\vec{f}}$
such that for all $X \in \mathbb{R}^{\left<\right>}$ it is true that
$G(X) = F(X[\left<\right>])$
Then,
\[ \frac{dF(x)}{dx} = \frac{dG(X)}{dX} \]
\end{theorem}
\begin{proof}
Let $\bar{f} \in \Dim(\vec{f})$ then for $F(x)[\vec{f}] = G(X)[\vec{f}]$.
Since $\partial F(x)[\vec{f}] / \partial x$ is defined as the rate of
change of $F(x)[\vec{f}]$ with respect to $x$, it stands to reason that,
$\partial F(X[\left<\right>])[\vec{f}] / \partial X[\left<\right>]$ is
equivalent by definition. By are given $G(X) = F(X[\left<\right>])$ we
can then also say that,
\[
\frac{ \partial F(X[\left<\right>])[\vec{f}] }{ \partial X[\left<\right>] }
=
\frac{ \partial G(X)[\vec{f}] }{ \partial X[\left<\right>] }
\]
Therefore, by our definitions of derivatives,
\[
\frac{ d F(x) }{ d x }
=
\frac{ d G(X) }{ d X }
\]
\end{proof}

@@

Let $f(X)$ be a function $f : \mathbb{R}^{\vec{x}} \to \mathbb{R}$. And let
$F(X)$ be an equivalent function,
$F : \mathbb{R}^{\vec{x}} \to \mathbb{R}^{\left<\right>}$
such that for all $X \in \mathbb{R}^{\vec{x}}$ it is true that
$F(X)[\left<\right>] = f(X)$
Then,
\[ \frac{df(X)}{dX} = \frac{dF(X)}{dX} \]
\end{theorem}
\begin{proof}
TODO
\end{proof}

@@

@@

\begin{definition}[Multimatrix Subtraction]
Let $A, B \in \mathbb{R}^{\vec{x}}$. Then,
\[ A - B = A + (-1)B \]
It should be obvious that, as with scalars, multimatrix subtraction is the
inverse of addition. In other words, $(A + B) - B = A$
\end{definition}

@@

\begin{theorem}[Communicativity of scalar Multiplication and Transposition]
\[ s\Tran(A, x) = \Tran(sA, x) \]
\end{theorem}
\begin{proof}
TODO
\end{proof}

\begin{theorem}[Stacked Transposition]
\[ \Tran(\Tran(A, x), y) = \Tran(A, x+y) \]
\end{theorem}
\begin{proof}
TODO
\end{proof}

\section*{Exercises}
TODO

>>>>

\newenvironment{argument}{\noindent\textit{Argument.}}{\hfill$\square$}

@@

\begin{displayquote}
``You can't just start a section with a subsection heading. At least put a quote
in there or something,'' - Dr. William Tepfenhart, my software architecture professor.
\end{displayquote}

@@

In other words, let $s \in \mathbb{R}$ and $S \in \mathbb{R}^{\left<\right>}$ such that
$S[\left<\right>] = s$. Then, for any multimatrix $A$, 
\[ sA = As = S \mmult{0} A = A \mmult{0} S \]
\end{theorem}
\begin{proof}
Let $|A| = \vec{a}$. Then for all $\bar{a} \in \Dim(\vec{a})$,
\begin{align*}
	(sA)[\bar{a}]
	&= (s)A[\bar{a}] \\
	&= A[\bar{a}](s) \\
	&= (As)[\bar{a}]
\end{align*}
So $sA = As$. Also,
\begin{align*}
	(sA)[\bar{a}]
	&= (s)A[\bar{a}] \\
	&= S[\left<\right>]A[\bar{a}] \\
	&= \sum_{\forall \bar{c} \in \Dim(\left<\right>)}
		S[\left<\right> \oplus \bar{c}]A[\bar{c} \oplus \bar{a}] \\
	&= \sum_{\forall \bar{c} \in \{\left<\right>\}}
		S[\left<\right> \oplus \bar{c}]A[\bar{c} \oplus \bar{a}] \\
	&= S[\left<\right> \oplus \left<\right>]A[\left<\right> \oplus \bar{a}] \\
	&= S[\left<\right>]A[\bar{a}] \\
	&= (S \mmult{0} A)[\left<\right> \oplus \bar{a}] \\
	&= (S \mmult{0} A)[\bar{a}] \\
\end{align*}
So, $sA = S \mmult{0} A$.
Finally, by similiar reasoning,
\begin{align*}
	(sA)[\bar{a}]
	&= (s)A[\bar{a}] \\
	&= A[\bar{a}](s) \\
	&= A[\bar{a}]S[\left<\right>] \\
	&= \sum_{\forall \bar{c} \in \Dim(\left<\right>)}
		A[\bar{a} \oplus \bar{c}] S[\bar{c} \oplus \left<\right>] \\
	&= \sum_{\forall \bar{c} \in \{\left<\right>\}}
		A[\bar{a} \oplus \bar{c}] S[\bar{c} \oplus \left<\right>] \\
	&= A[\bar{a} \oplus \left<\right>] S[\left<\right> \oplus \left<\right>] \\
	&= A[\bar{a}]S[\left<\right>] \\
	&= (A \mmult{0} S)[\bar{a} \oplus \left<\right>] \\
	&= (A \mmult{0} S)[\bar{a}]
\end{align*}
So $sA = A \mmult{0} S$. Therefore we've shown that
$sA = As = S \mmult{0} A = A \mmult{0} S$
\end{proof}

@@

Let $F(x)$ be a function $F : \mathbb{R} \to \mathbb{R}^{\vec{f}}$. And let
$G(X)$ be an equivalent function,
$G : \mathbb{R}^{\left<\right>} \to \mathbb{R}^{\vec{f}}$
such that for all $X \in \mathbb{R}^{\left<\right>}$ it is true that
$G(X) = F(X[\left<\right>])$
Then,
\[ \frac{dF(x)}{dx} = \frac{dG(X)}{dX} \]
\end{theorem}
\begin{argument}
Let $\bar{f} \in \Dim(\vec{f})$ then for $F(x)[\vec{f}] = G(X)[\vec{f}]$.
Since $\partial F(x)[\vec{f}] / \partial x$ is defined as the rate of
change of $F(x)[\vec{f}]$ with respect to $x$, it stands to reason that,
$\partial F(X[\left<\right>])[\vec{f}] / \partial X[\left<\right>]$ is
equivalent by definition. By are given $G(X) = F(X[\left<\right>])$ we
can then also say that,
\[
\frac{ \partial F(X[\left<\right>])[\vec{f}] }{ \partial X[\left<\right>] }
=
\frac{ \partial G(X)[\vec{f}] }{ \partial X[\left<\right>] }
\]
Therefore, by our definitions of derivatives,
\[
\frac{ d F(x) }{ d x }
=
\frac{ d G(X) }{ d X }
\]
\end{argument}

@@

Let $f(X)$ be a function $f : \mathbb{R}^{\vec{x}} \to \mathbb{R}$. And let
$F(X)$ be an equivalent function,
$F : \mathbb{R}^{\vec{x}} \to \mathbb{R}^{\left<\right>}$
such that for all $X \in \mathbb{R}^{\vec{x}}$ it is true that
$F(X)[\left<\right>] = f(X)$
Then,
\[ \frac{df(X)}{dX} = \frac{dF(X)}{dX} \]
\end{theorem}
\begin{argument}
Let $\bar{x} \in \Dim(\vec{x})$. We note that as $\partial f(X) / \partial X[\bar{x}]$
is defined as the rate of change of $f(X)$ as $X[\bar{x}]$ changes, and each value of
$f(X)$ is equal to $F(X)[\left<\right>]$, we can reason that the rate of change of
$F(X)[\left<\right>]$ as $X[\bar{x}]$ changes is equal to the rate of change of $f(X)$
as $X[\bar{x}]$ changes. That is,
\[
	\frac{\partial f(X)}{\partial X[\bar{x}]}
		=
	\frac{\partial F(X)[\left<\right>]}{\partial X[\bar{x}]}
\]
And so by our definition of derivatives,
\[ \frac{df(X)}{dX} = \frac{dF(X)}{dX} \]
\end{argument}

@@

Ah addition. What can I say about multimatrix addition that hasn't been
said so many times before. Well... anything, actually. I don't think anyone's
written about multimatrix addition before. Probably should define it first
though.

@@

Multimatrix subtraction is defined as the inverse of multimatrix addition.

\begin{definition}[Multimatrix Subtraction]
Let $A, B \in \mathbb{R}^{\vec{x}}$. Then,
\[ (A + B) - B = A \]
\end{definition}

The following should be obvious,

\begin{theorem}[Equivalent Addition for Subtraction]
\label{eq_add_sub_thm}
For any multimatricies $A$ and $B$ where $|A| = |B|$,
\[ A - B = A + (-1)B \]
\end{theorem}
\begin{proof}
Left as an exercise for the reader (Exercise \ref{eq_add_sub_ex}).
\end{proof}

@@

\begin{theorem}[Communicativity of scalar Multiplication and Transposition]
Let $s$ be a scalar, $x$ be in $\mathbb{Z}^{+} \cup \{0\}$, and $A$ be
a multimatrix on which $\Tran(A, x)$ is defined. Then,
\[ s\Tran(A, x) = \Tran(sA, x) \]
\end{theorem}
\begin{proof}
Let $|A| = \vec{x} \oplus \vec{a}$ where $|\vec{x}| = x$. Then
let $\bar{x} \in \Dim(\vec{x})$ and $\bar{a} \in \Dim(\vec{a})$. So,
\begin{align*}
  (s\Tran(A, x))[\bar{a} \oplus \bar{x}]
  &= s \Tran(A, x)[\bar{a} \oplus \bar{x}] \\
  &= s A[\bar{x} \oplus \bar{a}] \\
  &= (s A)[\bar{x} \oplus \bar{a}] \\
  &= \Tran(sA, x)[\bar{a} \oplus \bar{x}]
\end{align*}
Therefore $s\Tran(A, x) = \Tran(sA, x)$.
\end{proof}

\begin{theorem}[Stacked Transposition]
\[ \Tran(\Tran(A, x), y) = \Tran(A, x+y) \]
\end{theorem}
\begin{proof}
Let $|A| = \vec{x} \oplus \vec{y} \oplus \vec{a}$ where $|\vec{x}| = x$ and
$|\vec{y}| = y$. Note that,
\[ |\Tran(A, x)| = \vec{y} \oplus \vec{a} \oplus \vec{x} \]
And,
\[ |\Tran(\Tran(A, x), y)| = \vec{a} \oplus \vec{x} \oplus \vec{y} \]
Also that,
\[ |\Tran(A, x+y)| = \vec{a} \oplus \vec{x} \oplus \vec{y} \]
So $|\Tran(\Tran(A, x), y)| = \Tran(A, x+y)$ which is necessary but not
sufficient for this proof.

To show the elementwise equivalence, let $\bar{x} \in \Dim(\vec{x})$,
$\bar{y} \in \Dim(\vec{y})$, and $\bar{a} \in \Dim(\vec{a})$. Then,
\begin{align*}
  \Tran(\Tran(A, x), y)[\bar{a} \oplus \bar{x} \oplus \bar{y}]
  &= A[\bar{x} \oplus \bar{y} \oplus \bar{a}] \\
  &= \Tran(A, x+y)[\bar{a} \oplus \bar{x} \oplus \bar{y}]
\end{align*}
Which shows that $\Tran(\Tran(A, x), y) = \Tran(A, x+y)$
\end{proof}

\begin{exercise}
\label{eq_add_sub_ex}
Prove Theorem \ref{eq_add_sub_thm}.
\end{exercise}

TODO
